MSE and dynamic state variable model with sigma function

### 2018-09-04 doc/MSE_MAR_18.tex
added some text to tex file

@@

\begin{itemize}
\item{Simultaneously implementation of MSY and LO objectives may lead to a very restrictive fishing activity, at least, in the short-term. Effort is constrained by some stock, as predicted, in general terms, by Ulrich et al. (2011).}
\item{Drastic reduction of effort would increase profits if MSY and LO were contemplated. However, no flexibilities or year transfer swaps were considered. Be carefull if applying flexibilities, because as Prellezo 2016 (the results obtained from applying any kind of exemption or flexibility are, simply, negative) said, any increased in mortality beyond the MSY would be negative.}
\item{once the status of the stock has been assessed relative to its MSY level, the calculation of a TAC comes automatically from the rules of the Management Procedure. Shifting areas toward complying TAC limitations produced changes in selectivity ant therefore, constant changes in MSY levels. (e.g. shifting selectivity toward smaller/younger fish will generally reduce MSY). if it is required that the TAC should correspond to the level where MSY can be obtained, it will be necessary to monitor continuously the stock abundance and to revise TACs on a regular basis.}
\item{The  MSY under two quota species may be below what was achieved in one quota species because overall selectivity has shifted to smaller fish and low harvest of older fish; the impact of this change in selectivity on estimates of MSY is clearly seen in the results from Fig. \ref{f:selectivity} and \ref{f:yields}. While  the  potential  MSY  has decreased over time the stock biomass required to produce this MSY has increased.}
\item{Catch quota management is a more important mechanism than the actual obligation to land. An accurate and monitoring of all catches is a primary step towards sustainable and responsible fisheries.}
\item{The compliance of the fleets, the changes in behaviour and the availability and reliability of catch statistics (Catchpole and Riveiro Santos, 2015) . Data risks should not be overlooked (Hentati-Sundberg et al., 2014). Fish stock assessment provides the foundation for scientific advice to decision-makers on sustainable catch levels. A critical feature of stock assessment methodology is its dependence on accurate commercial data, which makes it susceptible to biased reporting (Walters and Maguire, 1996; Cotter et al., 2004; Bousquet et al., 2010). The reasons for misreporting and underreporting include e.g. IUU fishing (Agnew et al., 2009), discard obligation (Kelleher, 2005; Wielgus et al., 2010) and catches from recreational fisheries (Zeller et al., 2011). Such misreporting can be driven by fishing fleet overcapacity, resulting from restrictive TACs and/or effort regulations (Patterson, 1998; Beare et al., 2005; Dobby et al., 2008) that create economic incentives for non-compliance (Sumaila et al., 2006; Gallic and Cox, 2006; Osterblom et al., 2011).}

>>>>

Some text about increased use of Management strategy evaluation, where the focus has often been on the populaiton dynamics of a single species (examples, key refs). However, the human dimension is equally imoprtant (paper Fulton 2011 in FaF, mayby Hilborn 1985). MSE with explicit human dim is emerging (Ono 2017,  Andersen et al.  2010). Here we use an MSE with DSVM, including location choice and population is hetorgeneous. This is especiallyt relevant

@@

\begin{itemize}
\item{in mixed fisheries, constraining quota for a single species brings risk of changing exploitation patterns, with younger fish being targeted for, hence eroding production potential of stocks}
\item{Simultaneously implementation of MSY and LO objectives may lead to a very restrictive fishing activity, at least, in the short-term. Effort is constrained by some stock, as predicted, in general terms, by Ulrich et al. (2011).}
\item{Drastic reduction of effort would increase profits if MSY and LO were contemplated. However, no flexibilities or year transfer swaps were considered. Be carefull if applying flexibilities, because as Prellezo 2016 (the results obtained from applying any kind of exemption or flexibility are, simply, negative) said, any increased in mortality beyond the MSY would be negative.}
\item{once the status of the stock has been assessed relative to its MSY level, the calculation of a TAC comes automatically from the rules of the Management Procedure. Shifting areas toward complying TAC limitations produced changes in selectivity ant therefore, constant changes in MSY levels. (e.g. shifting selectivity toward smaller/younger fish will generally reduce MSY). if it is required that the TAC should correspond to the level where MSY can be obtained, it will be necessary to monitor continuously the stock abundance and to revise TACs on a regular basis.}
\item{The  MSY under two quota species may be below what was achieved in one quota species because overall selectivity has shifted to smaller fish and low harvest of older fish; the impact of this change in selectivity on estimates of MSY is clearly seen in the results from Fig. \ref{f:selectivity} and \ref{f:yields}. While  the  potential  MSY  has decreased over time the stock biomass required to produce this MSY has increased.}
\item{Catch quota management is a more important mechanism than the actual obligation to land. An accurate and monitoring of all catches is a primary step towards sustainable and responsible fisheries.}
\item{The compliance of the fleets, the changes in behaviour and the availability and reliability of catch statistics (Catchpole and Riveiro Santos, 2015) . Data risks should not be overlooked (Hentati-Sundberg et al., 2014). Fish stock assessment provides the foundation for scientific advice to decision-makers on sustainable catch levels. A critical feature of stock assessment methodology is its dependence on accurate commercial data, which makes it susceptible to biased reporting (Walters and Maguire, 1996; Cotter et al., 2004; Bousquet et al., 2010). The reasons for misreporting and underreporting include e.g. IUU fishing (Agnew et al., 2009), discard obligation (Kelleher, 2005; Wielgus et al., 2010) and catches from recreational fisheries (Zeller et al., 2011). Such misreporting can be driven by fishing fleet overcapacity, resulting from restrictive TACs and/or effort regulations (Patterson, 1998; Beare et al., 2005; Dobby et al., 2008) that create economic incentives for non-compliance (Sumaila et al., 2006; Gallic and Cox, 2006; Osterblom et al., 2011).}
